---
title: "Working Memory Development and Crashes: MLR Multiverse Analysis"
author: "Dan Mirman"
date: "`r Sys.Date()`"
output: pdf_document
---

These are updated analyses run following in-principle acceptance in *Coretx*. Key changes/updates:

* added Gender to set of covariates
* added CFA scores to composite method

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(effects)
library(broom.mixed)
library(knitr)
#library(patchwork)

# read in data
load("../WM_crash_N118_2020-11.RData")
```

```{r echo=FALSE, fig.height=3, fig.width=7, message=FALSE, warning=FALSE}
pivot_longer(dat_comp_cfa, cols=c(StdScoreM, StdScoreM_CB, StdScore_CFA),
             names_to = "Std_Type") %>%
  mutate(Std_Type = factor(Std_Type, labels = c("CFA", "Within Wave", "Common Baseline"))) %>% 
  ggplot(aes(Time, value, color=Group)) + 
  facet_wrap(~ Std_Type) +
  stat_summary(fun.data = mean_se, geom="pointrange") + 
  stat_smooth(method = "lm", se=FALSE) +
  theme_bw() + labs(y="WM Composite Score")
```

## MLR Multiverse

These are multilevel regression (MLR) versions of the analyses of the association between WM development trajectory and crashes. The multiverse examines three main decision points:

* WM measurement model (standardisation): within-wave vs. common-baseline
    + Walshe et al. used within-wave
    + Common-baseline more transparently represents the development pattern
    + A longitudinal CFA model
* Inclusion of covariates: yes vs. no
    + Walshe et al. included covariates
    + Covariates had minimal effects so excluding them may produce a more parsimonious model
* Selection of waves: 1-6 vs. 2-6 vs. 1-5
    + Walshe et al. used waves 2-6
    + Using all waves (1-6) includes more data 
    + Using waves 1-5 omits the post-crash WM assessment

### Results
```{r run_models_funct, echo=FALSE}
my_tidy <- function(m){
  #a slight variant of tidy() to keep track of convergence issues
  result <- cbind(tidy(m), 
  Convergence = is_empty(m@optinfo$conv$lme4))
}
run_models <- function(dat){
  # function to run a quartet of models on the same data set
  # model 1: within-wave std
  m.ww <- lmer(StdScoreM ~ Gender + Reckless + Driving_Errors + Risk_Behav +
                         Time*Group + (Time | ID),
                       data = dat, REML = FALSE)
  # model 2: remove covariates
  m.ww_nocov <- update(m.ww, . ~ Time*Group + (Time | ID))
  # model 3: common baseline
  m.cb <- update(m.ww, StdScoreM_CB ~ .)
  # model 4: CB remove covariates
  m.cb_nocov <- update(m.cb, . ~ Time*Group + (Time | ID))
  # model 5: CFA
  m.cfa <- update(m.ww, StdScore_CFA ~ .)
  # model 6: CFA remove covariates
  m.cfa_nocov <- update(m.cfa, . ~ Time*Group + (Time | ID))
  # extract key term info
  result <- list(m.ww, m.ww_nocov, m.cb, m.cb_nocov, m.cfa, m.cfa_nocov) %>% 
    plyr::ldply(., .fun="my_tidy") %>% 
    filter(term == "Time:GroupNever_Crashed") %>% 
    mutate(Standardisation = rep(c("Within_Wave", "Common_Baseline", "CFA"),
                                 each=2),
           Covariates = rep(c("Yes", "No"), 3)) %>% 
    select(-effect, -group) %>% 
    select(Standardisation, Covariates, everything())
  return(result)
}
```

```{r prep_data, echo=FALSE, warning=FALSE, message=FALSE}
# main data set for models
dat.all <- subset(dat_comp_cfa, Group != "Non_Driver")
tmp <- list(dat.all, # all waves
            subset(dat.all, Time > 0), # drop wave 1
            subset(dat.all, Time < 6)) %>% # drop wave 6
  plyr::ldply(., .fun="run_models") %>% 
  mutate(Waves = rep(c("1-6", "2-6", "1-5"), each=6)) %>% 
  select(Waves, everything())
```

```{r echo=FALSE}
kable(select(tmp, -term, -df), digits = 3)
tmp %>% mutate(Waves = str_replace(Waves, "-", "_")) %>% 
         write_csv("MLR_MVresults.csv")
```
